This is the Title

### 2017-04-20 paper/paper-DrexelFormat.tex
little fixes in the paper

% ====================================================================================================================================
% ====================================================================================================================================
\chapter{Background}\label{sec:bg}
% ====================================================================================================================================
% ====================================================================================================================================
This chapter presents the necessary background to understand the experiments presented later in the paper. This chapter is dived to three sections. First section \ref{sec:DL} covers basic deep learning including recurrent neural network and auto-encoder. Second section \ref{sec:DLL} compares deep learning libraries: DL4J, Theano, and Tensorflow. The last section \ref{sec:MLDD} introduces current trend of machine learning with driving data.

\section{Deep Learning}\label{sec:DL}
This section covers basic concept of deep learning. First subsection \ref{subsec:basicDL} introduces to deep learning, and next section \ref{subsec:RNN} deals with recurrent neural network and long short term memory neural network. The last subsection \ref{subsec:AE} covers auto-encoder.

\subsection{Basic Concept}\label{subsec:basicDL}
This part Explain basic deep learning

@@

\begin{enumerate}
\item Basic concept of recurrent neural network

	A recurrent neural network (RNN) is a neural network that is specialized for processing a sequence of input values \cite{Goodfellow-et-al-2016}. The figure \ref{fig:RNN} illustrates abstract structure of RNN. RNN has two input. One input is from data such as normal neural network input but another input is from previous output and the property gives benefit for sequential input data. This is because past output affects to current output. With sequential data, previous data can affect to current data and RNN considers previous output for current output. It means that even input from data are equal if previous output are different, current output are also different.

@@

	To describe RNN in math equation, let $x^{t}$ be input data on time $t$, $h^{t}$ be result from hidden layer on time $t$, and $o^{t}$ be output on time $t$. The tensor $U$ is a set of neurons for input data, The tensor $V$ is a set of neurons for data from hidden layer and the tensor $W$ is a set of neurons for previous output. The figure \ref{fig:unfold_RNN} illustrates unfolded RNN with defined symbols. The result from hidden layer can be calculated by 
	$$h^{t} = f(Ux^{t} + Wo^{t-1} + b_h)$$ where $f()$ is activation function for hidden layer and $b$ is bias for hidden layer. Then the output can be calculated by
	$$o^{t} = g(Vh^{t}+b_o)$$ where $g()$ is activation function for output layer and $b_o$ is bias for output layer. Therefore, RNN can be written in
	$$o^{t} = g(Vf(Ux^{t} + Wo^{t-1} + b_h) + b_o)$$

@@

	Basic RNN has problem of long term dependency. It means that RNN is not able to memorize long term knowledge. To solve the problem, LSTM is introduced by Hochreiter and Schmidhuber \cite{hochreiter1997long}. LSTM has cell state and it solves long term memory problem in RNN because cell state can store long term memory {\color{red} [santi: explain what is ``cell state'']}.

>>>>

% ====================================================================================================================================
% ====================================================================================================================================
\chapter{Background}\label{sec:bg}
% ====================================================================================================================================
% ====================================================================================================================================
This chapter presents the necessary background to understand the experiments presented later in the paper. This chapter is dived to three sections. First Section \ref{sec:DL} covers basic deep learning including recurrent neural network and auto-encoder. Second Section \ref{sec:DLL} compares deep learning libraries: DL4J, Theano, and Tensorflow. The last Section \ref{sec:MLDD} introduces current trend of machine learning with driving data.

\section{Deep Learning}\label{sec:DL}
This section covers basic concept of deep learning. First Subsection \ref{subsec:basicDL} introduces to deep learning, and next Section \ref{subsec:RNN} deals with recurrent neural network and long short term memory neural network. The last Subsection \ref{subsec:AE} covers auto-encoders.

\subsection{Basic Concepts}\label{subsec:basicDL}
{\color{blue} This part Explain basic deep learning [...]}

@@

\begin{enumerate}
\item Basic concepts of recurrent neural networks:

	A recurrent neural network (RNN) is a neural network that is specialized for processing a sequence of input values \cite{Goodfellow-et-al-2016}. Figure \ref{fig:RNN} illustrates abstract structure of RNN. RNN has two input. One input is from data such as normal neural network input but another input is from previous output and the property gives benefit for sequential input data. This is because past output affects to current output. With sequential data, previous data can affect to current data and RNN considers previous output for current output. It means that even input from data are equal if previous output are different, current output are also different.

@@

	To describe RNN in math equation, let $\vec{x}^t = \{ x_1^t, ..., x_n^t\} \in \mathbb{R}^n$ be a vector that represents the input data at time $t$, $h^{t} = \{ h_1^t, ..., h_m^t\} $ be result from hidden layer on time $t$, and $o^{t}$ be output on time $t$. The tensor $U$ is a set of neurons for input data, The tensor $V$ is a set of neurons for data from hidden layer and the tensor $W$ is a set of neurons for previous output. The figure \ref{fig:unfold_RNN} illustrates unfolded RNN with defined symbols. The result from hidden layer can be calculated by 
	$$h^{t} = f(Ux^{t} + Wo^{t-1} + b_h)$$ where $f()$ is activation function for hidden layer and $b$ is bias for hidden layer. Then the output can be calculated by
	$$o^{t} = g(Vh^{t}+b_o)$$ where $g()$ is activation function for output layer and $b_o$ is bias for output layer. Therefore, RNN can be written in
	$$o^{t} = g(Vf(Ux^{t} + Wo^{t-1} + b_h) + b_o)$$

@@

	Basic RNN have the problem of long term dependency. It means that an RNN is not able to memorize long term knowledge. To solve the problem, LSTMs were introduced by Hochreiter and Schmidhuber \cite{hochreiter1997long}. An LSTM has a cell state and it solves the long term memory problem in RNN because cell state can store long term memory {\color{red} [santi: explain what is ``cell state'']}.
